---
title: "ISLR Ch 3 & 4"
author: "Kathleen Johnson"
date: "12/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rlang)
library(tidyverse)

```


```{r}

boston <- MASS::Boston
```


 Is there a non-linear relationship between crime rate (y) variable name "crim", and average age of houses (x) variable name "age"?
 
```{r}
ggplot(data = boston) + 
  geom_point(mapping = aes(x = age, y = crim))
```
 
```{r}
summary(boston$age)
```
 
 Checking to see if I can even make the example work:
```{r}
lm.fit=lm(medv∼lstat , data=boston)

```


```{r}
lm(formula = medv ∼ lstat, data=boston)
```
 
```{r}
summary (lm.fit)
```
 
 
 Now to look at crime and age of house: 
```{r}
lm.fit=lm(crim∼age , data=boston)
```
 
```{r}
lm(formula = crim ∼ age, data=boston)
```
 
```{r}
summary (lm.fit)
```
 
```{r}
coef(lm.fit)
```
 
 Obtain confidence interval for the coefficient estimates
```{r}
confint (lm.fit)
```
 
```{r}
summary(boston$age)
```

So the 95% confidence interval associated with age of the house value of 3.25 years is (2.54, 3.96).
 
```{r}
predict (lm.fit ,data = boston(age=c(5,50 ,100)),
interval ="confidence")
```
 
The 95% prediction interval associated with age of the house value of 3.25 years is (-12.59, 19.09).
 
```{r}
predict (lm.fit ,data = boston(age=c(5,50 ,100)),
interval ="prediction")
```
```{r}
predict (lm.fit ,data.frame(age=c(50)),
interval ="prediction")
```

When age of the house is 50 the predicted crime rate is 1.61 (-14.24, 17.46).
```{r}
predict (lm.fit ,data.frame(age=c(50)),
interval ="confidence")
```

```{r}
boston$age2 <- boston$age^2
```

```{r}
summary(boston$age2)
```

 